Blueprint for efficient nuclear spin characterization in color center

### 2024-01-30 article.tex

\begin{abstract}
Nuclear spins in solids is one of the most promising platforms for realisation of a scalable quantum hardware. They could be efficiently addressed at single site level by nearby single colour centers via the spin resonance. However, characterising each nuclear spin is quite cumbersome as the characterisation protocol may differ depending on the strength of the hyperfine coupling. The most adopted protocol is modified electron spin Hahn-echos such as CPMG and XY8 pulse sequences. In some cases, e.g. for spin 1/2, strongly coupled spins, and bispecies bath this protocol contains severe problems in applying for the nuclear spin bath characterisation. 
Here, we present a more straight forward method to obtain hyperfine interaction among nuclear spins and the electron spin. 
This method can be used for a variety of platform including emerging S=1/2 group IV defects in diamond (e.g. SiV, GeV, SnV, PbV) or Silicon vacancy in Silicon Carbide.
We summarize theoretical framework and adopt it from ESR for the use in colour centers with various spins, and numerically consider case of nuclear spin cluster, as compare performance of various protocols on this example via the Fisher information matrix. 
\end{abstract}

@@

\section{Discussion}
\label{sec:discussion}
%\subsection{Advanced filters}
Here is the concise conclusion @Vadim

>>>>

\begin{abstract}
Nuclear spins in solids is one of the most promising platforms for realisation of a scalable quantum hardware. They could be efficiently addressed at single site level by nearby single colour centers via the spin resonance. However, characterising each nuclear spin is quite cumbersome as the characterisation protocol may differ depending on the strength of the hyperfine coupling. The most adopted protocol is modified electron spin Hahn-echos such as CPMG and XY8 pulse sequences. In some cases, e.g. for spin 1/2, strongly coupled spins, and bispecies bath this protocol suffers severe problems when applied for the nuclear spin bath characterisation. 
Here, we present a more straight forward method to obtain hyperfine interaction among nuclear spins and the electron spin. 
This method can be used for a variety of platform including emerging S=1/2 group IV defects in diamond (e.g. SiV, GeV, SnV, PbV) or Silicon vacancy in Silicon Carbide.
We summarize theoretical framework and adopt it from ESR for the use in colour centers with various spins, and numerically consider case of nuclear spin cluster for performance comparison of various protocols on this example via the Fisher information matrix as a metric. 
\end{abstract}

@@

\section{Discussion}
\label{sec:discussion}
%\subsection{Advanced filters}
Here is the concise conclusion
